Extracting the transcripts of the 'Ibizia Inquiry

### 2021-10-07 _post/2021-07-18-the-ibizia-inquiry-in-numbers/the-ibizia-inquiry-in-numbers.Rmd
update index

---
title: "Extracting the transcripts of the 'Ibizia Inquiry'"
description: In mid-June, the so-called 'Ibiza Commission of Inquiry' heard its last witness after almost one year at work. The commission had been established by the Austrian Parliament and set up to investigate the prevalence of corruption during the coalition government of the ÖVP and FPÖ (Dec, 2017- May, 2019). This post diggs into its published transcripts. The emphasis of the post is, first, on demonstrating how to extract the text from the hearings' transcripts in R and, second, on crunching a few numbers to get some substantive insights. The compiled dataset, covering all statements (incl. questions, answers etc.), is available for download.

>>>>

---
title: "Extracting the transcripts of the 'Ibizia Inquiry'"
description: In mid-June, the so-called 'Ibiza Commission of Inquiry' heard its last witness after almost one year at work. The commission had been established by the Austrian Parliament and set up to investigate the prevalence of corruption during the coalition government of the ÖVP and FPÖ (Dec, 2017 - May, 2019). This post diggs into its published transcripts. The emphasis of the post is, first, on demonstrating how to extract the text from the hearings' transcripts in R and, second, on crunching a few numbers to get some substantive insights. The compiled dataset, covering all statements (incl. questions, answers etc.), is available for download.
